---
title: "Topic: Data types and structures. PRACTISE 3.2"
output: html_document
date: "2024-10-10"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




library(tidyr)


# Creating the initial data frame with plant heights at the start and end of the experiment

```{r eval = FALSE}
df <- data.frame(
  plant = c("plant 1", "plant 2", "plant 3", "plant 4", "plant 5"),
  start_experiment = c(12.0, 15.5, 10.2, 13.5, 14.8),
  end_experiment = c(14.0, 16.2, 9.5, 14.0, 15.3)
)
```
# Reshaping the data frame to have the height in one column and the time of the measurement as a factor
```{r eval = FALSE}
df_melted <- gather(df, key = "time", value = "height", start_experiment, end_experiment)
df_melted$time <- factor(df_melted$time)
```

# Creating the growth list
```{r eval = FALSE}
row_names <- rownames(df)
initial_heights <- df$start_experiment
final_heights <- df$end_experiment

```
# Calculating the percentage change in height for each plant
```{r eval = FALSE}
growth_percentage <- ((final_heights - initial_heights) / initial_heights) * 100
```
# Creating a table with plants and their corresponding growth
```{r eval = FALSE}
growth_table <- data.frame(
  plant = df$plant,
  growth = growth_percentage
)
```

# Creating the 'my.experiment' list
```{r eval = FALSE}
my.experiment <- list(
  data = df_melted,
  growth = list(
    plants = row_names,
    growth_percentage = growth_percentage,
    growth_table = growth_table
  ),
  message = "The plants have varying growth, with some increasing and others decreasing in height."
)
```
# Print the results
```{r eval = FALSE}
print(my.experiment)
```