---
title: "Practice 7.4"
output: html_document
date: "2024-11-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r eval = FALSE}
library(dplyr)
```
# Load the dataset 
```{r eval = FALSE}
url <- "https://www.dipintothereef.com/uploads/3/7/3/5/37359245/rairuoho.txt"
rairuoho <- read.table(url, header = TRUE)
```
# Pearson test function
```{r eval = FALSE}
pearson.test <- function(x, y) {
 
  r <- cor(x, y)
  n <- length(x)
  df <- n - 2
  t_value <- r * sqrt(df / (1 - r^2))
  p_value <- 2 * pt(-abs(t_value), df)
  result <- list(correlation = r, t_value = t_value, df = df, p_value = p_value)
  return(result)
}
```


# Apply the custom pearson.test function to test correlation in each treatment group (nutrient and water) and calculate correlations

```{r eval = FALSE}
# Nutrient
nutrient_data <- subset(rairuoho, treatment == "nutrient")
nutrient_corr_day3_day4 <- pearson.test(nutrient_data$day3, nutrient_data$day4)
nutrient_corr_day3_day8 <- pearson.test(nutrient_data$day3, nutrient_data$day8)

# Water 
water_data <- subset(rairuoho, treatment == "water")
water_corr_day3_day4 <- pearson.test(water_data$day3, water_data$day4)
water_corr_day3_day8 <- pearson.test(water_data$day3, water_data$day8)
```

# Results summary
```{r eval = FALSE}
cat("Nutrient Treatment:\n")
cat("Day 3 & Day 4 Correlation:", nutrient_corr_day3_day4$correlation, "\n",
    "t-value:", nutrient_corr_day3_day4$t_value, "\n",
    "p-value:", nutrient_corr_day3_day4$p_value, "\n\n")

cat("Day 3 & Day 8 Correlation:", nutrient_corr_day3_day8$correlation, "\n",
    "t-value:", nutrient_corr_day3_day8$t_value, "\n",
    "p-value:", nutrient_corr_day3_day8$p_value, "\n\n")

cat("Water Treatment:\n")
cat("Day 3 & Day 4 Correlation:", water_corr_day3_day4$correlation, "\n",
    "t-value:", water_corr_day3_day4$t_value, "\n",
    "p-value:", water_corr_day3_day4$p_value, "\n\n")

cat("Day 3 & Day 8 Correlation:", water_corr_day3_day8$correlation, "\n",
    "t-value:", water_corr_day3_day8$t_value, "\n",
    "p-value:", water_corr_day3_day8$p_value, "\n")
```   
# Interpretation of Results:

## Correlation Strength and Significance: function output will provide the Pearson correlation coefficient (r), degrees od freedom, t-value, and p-value for each pair of days (day 3 & day 4 and day 3 & day 8) within both treatments (nutrient and water).
## P-Value Interpretation: if the p-value is below a significance level, it indicates that there is a statistically significant correlation between the variables.












